### 2017-01-23 thesis/results/results.tex
tmp commit

\chapter{Obesity-associated genetic signatures and cancer}
\label{cha:obesity_genetic_signatures_and_cancer}

\section{Obesity-associated genetic signature from \citet{Creighton2012} study}
\label{sec:creighton_obesity_metagene}

\section{Obesity-associated genetic signature from \citet{Fuentes-Mattei2014} study}
\label{sec:fm_obesity_metagene}

@@

\section{Pathways enriched in obesity-associated genes}
\label{sec:pathways_enriched_in_obesity_associated_genes}

>>>>

\chapter{Obesity associated genetic signatures and cancer}
\label{cha:obesity_genetic_signatures_and_cancer}

In this chapter, the relationship between the obesity associated genetic signatures from previous studies and different cancer types were investigated; new obesity associated genetic signatures were identified in the data set from \citet{Creighton2012} study; and the presence of common genes or pathways across different cancer types was examined.

\section{Obesity associated genetic signature from \citet{Creighton2012} study}
\label{sec:creighton_obesity_metagene}

% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.8\linewidth]{intro/hallmarks}
% 	\caption[Hallmarks of Cancer]{Hallmarks of Cancer. The ten Hallmarks of Cancer as proposed by Hanahan and Weinberg in 2011. (Figure adapted from \citet{Hanahan2011})}
% 	\label{fig:hallmarks}
% \end{figure}

\section{Obesity associated genetic signature from \citet{Fuentes-Mattei2014} study}
\label{sec:fm_obesity_metagene}

\section{New obesity associated genetic signature in \citet{Creighton2012} data set}
\label{sec:creighton_obesity_metagene_new}

@@

\section{Pathways enriched in obesity associated genes}
\label{sec:pathways_enriched_in_obesity_associated_genes}

### 2017-01-23 thesis/results/results2.tex
Starting the write up of the first part of the results
tmp commit

\chapter{Results from gatza pathway metagene and direction stuff}

\section{Reproducing results from gatza paper}

>>>>

\chapter{Obesity associated genetic signatures and pathway signatures}
\label{cha:obesity_associated_genetic_signature_and_pathway_signatures}

In this chapter, the relationship between the obesity-associated genetic signatures from previous studies and different cancer types were investigated; new obesity-associated genetic signatures were identified in the data set from \citet{Creighton2012} study; and the presence of common genes or pathways across different cancer types was examined.
